Residuals in zinbwave, all genes

### 2017-06-02 R/zinbwave_residuals_all.Rmd

---
title: "Residuals in zinbwave, 1000 most variable genes"
author: "Fanny Perraudeau, Davide Risso"
date: "05/25/2017"
output: 
  html_document: 
    fig_height: 7
    fig_width: 7
    toc: yes
    code_folding: hide
    toc_float: yes
---

@@

Here we only look at the 1000 most variable genes.
```{r filtering}
names(batch) <- colnames(counts)

@@

vars <- rowVars(log1p(counts))
names(vars) <- rownames(counts)
vars <- sort(vars, decreasing = TRUE)
core <- counts[names(vars)[1:1000],]
```

@@

```{r}
heatmap.2(Rn[de_1000, ],
          col = colorRampPalette(c('blue', 'yellow'))(51),
          scale = 'none', trace = 'none',
          ColSideColors = as.character(clus.labels),
          labCol = '', main = 'Naive Residuals')
```

@@

```{r}
breaks = setBreaks(Rn[de_1000, ], breaks = 0.99)
heatmap.2(Rn[de_1000, ], breaks = breaks,
          col = colorRampPalette(c('blue', 'yellow'))(51),
          scale = 'none', trace = 'none',
          ColSideColors = as.character(clus.labels),
          labCol = '', main = 'Naive residuals')
```

@@

```{r}
heatmap.2(Rn[de_1000, ],
          col = colorRampPalette(c('blue', 'yellow'))(51),
          scale = 'none', trace = 'none',
          ColSideColors = as.character(clus.labels),
          labCol = '', main = 'Naive residuals')
```

>>>>

---
title: "Residuals in zinbwave, all genes"
author: "Fanny Perraudeau, Davide Risso"
date: "05/25/2017"
output: 
  html_document: 
    fig_height: 7
    fig_width: 7
    toc: yes
    code_folding: hide
    toc_float: yes
---

@@

Here we only look at all the genes.
```{r filtering}
names(batch) <- colnames(counts)

@@

#vars <- rowVars(log1p(counts))
#names(vars) <- rownames(counts)
#vars <- sort(vars, decreasing = TRUE)
#core <- counts[names(vars)[1:1000],]
core = counts
```

@@

```{r}
heatmap.2(Rn[de_1000, ], breaks = breaks,
          col = colorRampPalette(c('blue', 'yellow'))(51),
          scale = 'none', trace = 'none',
          ColSideColors = as.character(clus.labels),
          labCol = '', main = 'Log naive residuals')
```

@@

@@

```{r}
Rn_order = Rn[, order(as.numeric(batch))]
col_order = as.numeric(batch)[order(as.numeric(batch))]
plotBoxplot(Rn_order, main = 'Boxplot of residuals\ncolor=batch',
            col = col_order)
```
```{r}
heatmap.2(Rn[de_1000, ], breaks = breaks,
          col = colorRampPalette(c('blue', 'yellow'))(51),
          scale = 'none', trace = 'none',
          ColSideColors = as.character(clus.labels),
          labCol = '', main = 'Log naive residuals')
```
